A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-17 paper/sections/analysis.tex
commit analysis and background
backgroup updates
RQ2 and RQ6 analysis and discussion

@@

>>>>

The core RBAC standard represents four elements such as roles, sessions, users, and permissions, and their relations. While this model is considered fundamental in any RBAC systems, this model can be extended to be applicable for emerging applications such as healthcare and mobile devices. Such extended RBAC models are formally presented to describe its behaviors. In the selected papers, researchers illustrate how an extended model incorporates new element based on the correct RBAC and describe their relations with pre-defined elements in the core RBAC.

We classify motivations behind RBAC extensions to these three categories:

\begin{itemize}
	\item Addition: an extended model incorporates additional elements with regards to context/constraints and their relations with existing elements of the core RBAC. Models in this category does not change the core model. We found OO papers in this category.
	\item Modification:  an extended model incorporates modification of existing features in the core RBAC. For example, changes of attribute relations such as role hierarchy is to show modification. For models in this category, changes occur within the core model. We found OO papers in this category.
	\item Combination: an extended model is combination of RBAC and an another access control model, which uses model-specific attributes and their relations such as task, team, purpose, organizational roles. For this combination, new association between attributes of two models should be introduced. Models in this category requires a new association between attributes of different access control models to work together. We found OO papers in this category.
\end{itemize}

@@

Since NIST proposed RBAC standard using propositional logic, researchers describe extended RBAC models using propositional logic. Given context, propositional logic is used to evaluate true or false based on specified rules and access control logic. As access control is typically evaluated to either true (Permit) or false (Deny) based on predicates, propositional logic is sufficient to describe key ideas and definitions. We found that OO papers of RBAC extensions use propositional logic to describe its extended model.
However, propositional logic has limitations. While this logic is simple, this logic does not support for reasoning about RBAC, which helps reduce the administrative complexity of associations such as user- role associations. An alternative logic to describe RBAC is first-order logic. This logic is sufficient to describe RBAC and extended RBAC. Moreover, this logic supports for concise and elegant formulation of the RBAC model and its relation.  First-Order logic is expressive enough to concisely represent access control systems. First-Order logic uses relations, variables, and quantifiers.

### 2013-04-17 paper/sections/core_rbac.tex
commit analysis and background
backgroup updates
RQ2 and RQ6 analysis and discussion

Since the basis for our review is extensions to the core model, we will describe the core model, associated entities and other terminology encountered across the space of our review.

@@

The NIST RBAC model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three types of RBAC models: core RBAC, hierarchal RBAC, and constrained RBAC. The four entities of the standard RBAC model are:

>>>>

The NIST RBAC model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three types of RBAC models: core RBAC, hierarchal RBAC, and constrained RBAC.
Since the basis for our review is extensions to the core model, we describe the core model, associated entities and other terminology encountered across the space of our review. Then, we describe hierarchal RBAC and constrained RBAC, which are developed by incoporating new features into the core RBAC.

@@

The four entities of the standard RBAC model are:
